\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}

### 2009-12-25 AffineLieAlgebras/InformalNotes/article.tex
test
Added V.D. notes

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm} 
\usepackage{pb-diagram}
\usepackage{ucs}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage[pdftex]{graphicx}
\pagestyle{plain}
\theoremstyle{definition} \newtheorem{Def}{Definition}
%\usepackage{verbatim} 
\newenvironment{comment}
{\par\noindent{\bf TODO}\\}
{\\\hfill$\scriptstyle\blacksquare$\par}

\begin{document}
\title{\textbf{{\Large {Recursive algorithm for the computation of branching coefficients of affine Lie algebras with applications in CFT}}}}
\author{Vladimir Lyakhovsky\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:lyakh1507@nm.ru \\
[5mm] Anton Nazarov \\
%EndAName
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:antonnaz@gmail.com\\
}
\maketitle

\begin{abstract}
  We present the recurrent relation for the branching coefficients of affine Lie algebras. Then we describe the algorithm for the decomposition of  integrable highest weight modules
of a simple Lie algebra with respect to its reductive subalgebra which is based upon this recurrent relation and present some examples. Also we discuss the appearance of branching coefficients in the physical models.
\end{abstract}

@@

The problem of the reduction of Lie algebra representation to the representations of the subalgebra is studied for several decades and has various applications in physics. In the context of finite-dimensional algebras it is important for the study of great unification models whilst the problem of the branching of the affine Lie algebras emerges in conformal field theory, for example, in the construction of the modular-invariant partition functions \cite{difrancesco1997cft}.

There exist several approaches to the computation of the branching coefficients which use the BGG
resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in 
\cite{kac1990idl},\cite{wakimoto2001idl}), the Schure function series \cite{fauser2006new}, the BRST
cohomology \cite{hwang1994general}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or the
combinatorial methods applied in \cite{feigin707principal}.

Usually only the embedding of the maximal reductive subalgebras is considered since the case of non-maximal subalgebra can be obtained using the chain of maximal subalgebras. In this paper we present the recurrent formula for the branching coefficients which generalises the recurrent relation of the paper \cite{ilyin812pbc} to the case of non-maximal reductive subalgebra. Using this relation we formulate simple explicit algorithm for the computation of the branching coefficients which is applicable to the non-maximal subalgebras of finite-dimensional and affine Lie algebras.

We show that our algorithm can be used in the study of the conformal embeddings where the central charge of the conformal field theory is preserved, but the computation in this case is simplified using physical requirements.

The paper is organised as follows. In the next subsection of the introduction we fix the notation used throughout the paper. Then in Section \ref{sec:recurr-form-branch} we derive the central recurrent formula for the anomalous branching coefficients and describe the algorithm for the decomposition of the integrable highest weight modules of algebra $\mathfrak{g}$ to the modules of a reductive subalgebra $\mathfrak{a}$ (subsection \ref{sec:algorithm}). In the next Section \ref{sec:examples} we present several examples and discuss some applications in the physical models (s. \ref{sec:phys-appl}). We conclude the paper with the review of results and discussion of possible future developments (s. \ref{sec:conclusion}).

@@

\section{Recurrent relation for branching coefficients}
\label{sec:recurr-form-branch}

We present the final recurrent relation for the anomalous branching coefficients \eqref{eq:21}. 
\begin{equation}
  \label{eq:1}
k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)   
\end{equation}
Here $\mathfrak{a}_{\bot}$ is the subalgebra generated by the roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$, $W_{\bot}$ is the corresponding Weyl group, $\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion of the product $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$ is the coefficient of $e^{\gamma}$ in this expansion.
The proof of the formula and more formal definitions of $\mathfrak{a}_{\bot},\; W_{\bot},\; s(\gamma),\; \Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ are in the following subsection.

In the next section we describe the algorithm for the computation of branching coefficients based upon this formula and then present some example and discuss physical meaning.

@@

The decomposition of the representation of the algebra to the representations of the subalgebra can be symbolically written using formal characters and projection operator $\pi_{\mathfrak{a}}$ to the weight subspace:
\begin{equation}
  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation}
Using the Weyl-Kac formula for the character of the module
we obtain the equality
\begin{equation}
  \label{eq:4}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = 
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{equation}

It is important to mention that the projection of some of the positive roots of the algebra $\mathfrak{g}$ can be equal to zero. These roots are orthogonal to the root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the algebra $\mathfrak{g}$. Let's denote the subset of these roots by $\Delta^{+}_{\bot}=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.

We should notice that if the set $\Delta^{+}_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$. Consider any two positive roots $\alpha,\; \beta\in \Delta^{+}_{\bot}$ and corresponding Weyl reflections $\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since roots of the subalgebra $\mathfrak{a}$ are invariant under $\omega_{\alpha}, \; \omega_{\beta}$ they are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$. So the subgroup $W_{\bot}$ preserves the root system of the subalgebra $\mathfrak{a}$.

The action of the Weyl subgroup $W_{\bot}$ on the set $\Delta^{+}_{\bot}$ produce the root system $\Delta_{\bot}$ which is orthogonal to the root system $\Delta_{\mathfrak{a}}$ of the subalgebra $\mathfrak{a}$. This root system can be considered as the root system of some subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.

Now we should discuss when the subset $\Delta^{+}_{\bot}$ is non-empty and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.

If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and it is clear that $\Delta^{+}_{\bot}$ is empty.
On the other hand 
non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained through the chain of maximal embeddings $\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$. Also the maximal regular embeddings are constructed by the exclusion of one or two roots from the extended Dynkin diagram of the algebra. Since this process can give us non-connected Dynkin diagrams we can see which roots are orthogonal to the root space of non-maximal regular subalgebra $\mathfrak{a}$.

Consider for instance regular embedding of $A_1\subset B_2$.

The extended Dynkin diagram of $B_2$ 
\begin{figure}[ph]
  \centering
  \includegraphics[width=50mm]{B2_A1_diagram.pdf}
  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
  \label{fig:B2Dynkin}
\end{figure}
We then drop central node and get the embedding $A_1\oplus A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.

Here we give the simple criterion of $\Delta^{+}_{\bot}$'s non-emptiness for the regular embedding $\mathfrak{a}\subset \mathfrak{g}$ for simple $\mathfrak{a}$ and $\mathfrak{g}$. If Dynkin diagram of $\mathfrak{g}$ can be split into the unconnected diagrams of $\mathfrak{a}$ and some other subalgebras $\{\mathfrak{\bar{a}}_j\}$ then the subset $\Delta_{\bot}$ is non-empty, subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and all the $\mathfrak{\bar{a}}_j$ are the subalgebras of $\mathfrak{a}_{\bot}$.

Note that when we study the regular embedding obtained by the dropping of the nodes of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the subalgebra $\mathfrak{a}$ is one of the connected components, the subalgebra $\mathfrak{a}_{\bot}$ may be broader than the algebra generated by the other connected components. See for example the figure \ref{fig:dynkin} for the embedding of $B_2\subset B_4$. 
In this case the extended Dynkin diagram of $B_4$ is split by dropping of simple root $\alpha_2=e_2-e_3$ into the diagrams of the subalgebra of interest $\mathfrak{a}=B_2$ and two diagrams of the orthogonal $A_1$ subalgebras. But the subalgebra $\mathfrak{a}_{\bot}$ is equal not to $A_1\oplus A_1$ but to $B_2$. 
This fact is due to the existence of positive root $e_2=s_{\alpha_2}\cdot s_{\alpha_3}\cdot\alpha_4$ in the root system of $B_4$.

We should analyze the case when the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$ for the simple Lie algebras $\mathfrak{a},\,\mathfrak{g}$ and the regular embedding $\mathfrak{a}\subset \mathfrak{g}$.
 We drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the rest nodes of the diagram of $\mathfrak{g}$ and consider the remaining diagram. This diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ of $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$. So the question is if $\mathfrak{a}_{\bot}$ has additional roots, which are not the roots of $\mathfrak{\bar{a}}$ but are the linear combinations of them. It is possible when the set of the angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$, then reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we the additional roots of $\mathfrak{a}_{\bot}$.

@@

In the language of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows. Given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}}; \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer of $W_{\mathfrak{a}}$ in $W$, such that some of the elements of $W_{\mathfrak{a}_{\bot}}$ are the reflections corresponding to the positive roots of $\mathfrak{g}$. This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} but we are unaware of any publication with the exhaustive tables of such a subgroups.

@@

\subsection{Affine Lie algebras}
\label{sec:affine-lie-algebras}
%%  \subsubsection{Embedding of finite-dimensional algebra into affine algebra}
%%  \label{sec:embedd-finite-dimens}
%%  
%%  The maximal embeddings of the finite-dimensional Lie algebras into the affine Lie algebras were thoroughly studied and the tables of the branching coefficients are given in the book \cite{kass1990ala}. The task of the study of non-maximal embeddings is then can be reduced to the well-known task of branching of the finite-dimensional Lie algebras.
%%  Thus here we show the simplest possible example of reduction of affine $\hat{A_1}$ to $A_1$ in order to demonstrate some traits of our method and show that we eliminate the need of slice-by-slice study discussed in \cite{kass1990ala}.
%%  
%%  The simple roots for the affine $\hat{A_1}$ are
%%  \begin{equation}
%%    \label{eq:2}
%%    (\alpha,\delta-\alpha)
%%  \end{equation}
%%  We consider the embedding with the root $\beta=\delta-\alpha$. 
%%  
%%  Positive roots of the $\hat{A_1}$ are $\alpha,\; \alpha+n\delta,\; n\delta,\; -\alpha+n\delta;\; n=1,2,3,\dots$.
%%  The set of the 
%%  
\subsubsection{Embedding of the affine algebra into affine algebra}
\label{sec:embedd-affine-algebr}

Consider the affine extension of the example \ref{sec:regul-embedd-a_1}. 
Since this embedding is regular, the level of the representations of the subalgebra is equal to the level of the representation of the algebra.

The set $\Delta^{+}_{\bot}$ of the orthogonal positive roots with the zero projection on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case.

Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0,1,0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the grade of the weight and the fourth is the level.

The set of the anomalous points of this representation up to sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the Figure \ref{fig:B2_A1}.

\begin{figure}[h!tb]
  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\hat{B_2}$}
  \label{fig:affine_B2_anom_point}
\end{figure}

As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of this computation up to the twelfth grade is presented at the Figure
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

Using the definition (\ref{fan-defined}) we get the following set of
the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$: \ref{fig:AffineB2A1Fan}.
Here we restricted the computation to the twelfth grade.
\begin{figure}[ph]
  \centering
  \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
  \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

Also we should mention that the lowest vector of the fan $\gamma_0$ is equal to zero, since we have excluded all the roots of $\Delta^{+}_{\bot}$ from the defining relation (\ref{fan-defined}).

Using the recurrent relation for the anomalous branching coefficients we get the following result
\begin{figure}[ph]
  \centering
  \includegraphics[width=130mm]{AffineB2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2_A1_branching}
\end{figure}

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm} 
\usepackage{pb-diagram}
\usepackage{ucs}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage[pdftex]{graphicx}
\pagestyle{plain}
\theoremstyle{definition} \newtheorem{Def}{Definition}

\begin{document} 
\thispagestyle{empty}

\begin{center}
{\Large \bf SAINT-PETERSBURG STATE\\[0.5cm] UNIVERSITY}
\end{center}
\vskip 1 cm
\begin{flushright}
{\large \bf SPbU-IP-09-0?}
\end{flushright}
\hfill {}
\vskip 1 cm
\begin{center}
{\Huge \bf Recursive algorithms, branching coefficients \\ for affine algebras and applications\\[0.5cm]
}
\end{center}
\vskip 1.0 cm
\begin{center}
{\Large \bf
Vladimir Lyakhovsky\\[2mm]
Anton Nazarov}
\end{center}
\vfill
\begin{center}
{\large Department of Theoretical Physics\\
}
\end{center}
\vfill
\begin{center}
SAINT-PETERSBURG \\
2009
\end{center}

\newpage

\title{\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}}
\author{Vladimir Lyakhovsky \thanks{ Supported by 
 RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575 }\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:lyakh1507@nm.ru \\
[5mm] Anton Nazarov \thanks{ Supported by
the National Project RNP.2.1.1./1575 }\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:antonnaz@gmail.com
}
\maketitle

\begin{abstract}
  Recurrent relations for branching coefficients in affine Lie algebras highest weight modules are studied. The decomposition algorithm for  integrable highest weight modules reduction based on the injection fan technique is adopted to the situation where the Weyl denominator becomes singular with respect to a reductive  subalgebra. We study some modifications of the injection fan technique and demonstrate that it is possible to define the "subtracted fans" that play the role similar to the original one. The possible applications of subtracted fans in CFT models are considered. 
\end{abstract}

@@

The problem of reduction of a Lie algebra representation to a  subalgebra is studied for several decades and has various applications in physics. In the context of finite-dimensional algebras it is important for the study of great unification models whilst the branching problem for affine Lie algebras emerges in conformal field theory, for example, in the construction of the modular-invariant partition functions \cite{difrancesco1997cft}.

There exist several approaches to the computation of the branching coefficients. Some of them use the BGG
resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in 
\cite{kac1990idl},\cite{wakimoto2001idl}), the Schure function series \cite{fauser2006new}, the BRST
cohomology \cite{hwang1994general}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or the
combinatorial methods applied in \cite{feigin707principal}.

Usually only the embedding of the maximal reductive subalgebras is considered since the case of non-maximal subalgebra can be obtained using the chain of maximal injections. In this paper we study the recurrent properties for branching coefficients which generalise the recurrent relations obtained earlier (see the paper \cite{ilyin812pbc}and the references therein) to the cases of non-maximal reductive subalgebras. The result is formulated by an introduction of a new injection fan called "subtracted fan". Using this new tools we formulate simple and explicit algorithm for the computation of branching coefficients which is applicable to the non-maximal subalgebras of finite-dimensional and affine Lie algebras.

We show that our algorithm can be used in a study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified taking into account some  physical limitations.

The paper is organised as follows. In the next subsection  we fix the notations used throughout the paper. In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous branching coefficients and describe the decomposition algorithm for integrable highest weight modules of algebra $\mathfrak{g}$ with respect to a reductive subalgebra $\mathfrak{a}$ (subsection \ref{sec:algorithm}). In the next Section \ref{sec:examples} we present several examples and discuss some applications in CFT models (s. \ref{sec:phys-appl}). We conclude the paper with a review of obtained results. Possible future developments are discussed (s. \ref{sec:conclusion}).

@@

\section{Recurrent relation for branching coefficients. Singularities and subtractions}
\label{sec:recurr-form-branch}

Our aim is to demonstrate that despite possible singularities in the Weyl denominator projected to the subalgebra root space injection fan technique can be properly modified. as a result of such modification the generalized recurrent relations for anomalous branching coefficients \eqref{eq:21} will appear in the following form: 
\begin{equation}
  \label{eq:1}
  \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
\left.
+\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)
  \end{array}
   \end{equation}
Here $\mathfrak{a}_{\bot}$ is the subalgebra generated by the roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$, $W_{\bot}$ is the corresponding Weyl group, $\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion of the denominator $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$ is the coefficient of $e^{\gamma}$ in this expansion.
In the next subsection we study the situation in details and prove the validity of this relation.

In the next section we  shall describe the  computational algorithm for  branching coefficients based on this formula and present some examples.

@@

The branching of a module can be symbolically written using formal characters and projection operators $\pi_{\mathfrak{a}}$ that bring the roots of $\mathfrak{g}$ to the weight subspace of $\mathfrak{a}$:
\begin{equation}
  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation}
The Weyl-Kac character formula leads to
the equality
\begin{equation}
  \label{eq:4}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = 
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{equation}

It is important to keep in mind that the projection of some of positive roots of the algebra $\mathfrak{g}$ can be equal to zero. These roots are orthogonal to the root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the algebra $\mathfrak{g}$. Let's denote the subset of such roots by $\Delta^{+}_{\bot}=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.

Notice that if the set $\Delta^{+}_{\bot}$ is non-empty the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of the Weyl group $W$. Consider any two positive roots $\alpha,\; \beta\in \Delta^{+}_{\bot}$ and the corresponding Weyl reflections $\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since roots of the subalgebra $\mathfrak{a}$ are invariant under $\omega_{\alpha}, \; \omega_{\beta}$ they are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$. So the subgroup $W_{\bot}$ preserves the root system of the subalgebra $\mathfrak{a}$.

Thus we have obtained the root system $\Delta_{\bot}$ which is orthogonal to the root system $\Delta_{\mathfrak{a}}$ and invariant with respect to  $W_{\bot}$ . This root system can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.

Now we should find out when the subset $\Delta^{+}_{\bot}$ is non-empty and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.

If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then the rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and it is clear that $\Delta^{+}_{\bot}$ is empty.
On the other hand 
non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained through the chain of maximal embeddings $\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$. The maximal regular embeddings are constructed by the exclusion of one or two roots from the extended Dynkin diagram of the algebra. Since this process can give us non-connected Dynkin diagrams we can see which roots are orthogonal to the root space of non-maximal regular subalgebra $\mathfrak{a}$.

Consider for instance regular the embedding of $A_1\subset B_2$.

The extended Dynkin diagram of $B_2$ is presented in the Figure 1.
\begin{figure}[ph]
  \centering
  \includegraphics[width=50mm]{B2_A1_diagram.pdf}
  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
  \label{fig:B2Dynkin}
\end{figure}
When we drop the central node and get the embedding $A_1\oplus A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.

Here we present the simple criterion of $\Delta^{+}_{\bot}$'s non-emptiness for a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ when both $\mathfrak{a}$ and $\mathfrak{g}$ are simple. If the Dynkin diagram of $\mathfrak{g}$ can be split into the disconnected diagrams of $\mathfrak{a}$ and some other subalgebras $\{\mathfrak{\bar{a}}_j\}$ then the subset $\Delta_{\bot}$ is non-empty, subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and all the $\mathfrak{\bar{a}}_j$ are the subalgebras of $\mathfrak{a}_{\bot}$.

Note that when we study the regular embedding obtained by dropping the nodes of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the subalgebra $\mathfrak{a}$ is one of the connected components, the subalgebra $\mathfrak{a}_{\bot}$ may be broader than the algebra generated by the other connected components. See for example the figure \ref{fig:dynkin} for the embedding of $B_2\subset B_4$. 
In this case the extended Dynkin diagram of $B_4$ is split by dropping the simple root $\alpha_2=e_2-e_3$ into the diagrams of the subalgebra of interest $\mathfrak{a}=B_2$ and two diagrams of the orthogonal $A_1$ subalgebras. But the subalgebra $\mathfrak{a}_{\bot}$ is equal not to $A_1\oplus A_1$ but to $B_2$. 
This fact is due to the existence of the positive root $e_2=s_{\alpha_2}\cdot s_{\alpha_3}\cdot\alpha_4$ in the root system of $B_4$.

We should analyze the case when the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$ for the simple Lie algebras $\mathfrak{a},\,\mathfrak{g}$ and the regular embedding $\mathfrak{a}\subset \mathfrak{g}$.
 We drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the rest nodes of the diagram of $\mathfrak{g}$ and consider the remaining diagram. This diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ of $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$. So the question is if $\mathfrak{a}_{\bot}$ has additional roots, which are not the roots of $\mathfrak{\bar{a}}$ but are the linear combinations of them. It is possible when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$, then reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$.

@@

In terms of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows. Given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}}; \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer of $W_{\mathfrak{a}}$ in $W$, such that some of the elements of $W_{\mathfrak{a}_{\bot}}$ are the reflections corresponding to the positive roots of $\mathfrak{g}$. This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} but we are unaware of any publication with the exhaustive tables of such subgroups.

@@
